---
title: "Classification Intro"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')

library(tidyverse) 
library(caret)
library(class)
library(patchwork)
library(tidymodels)
library(mlbench)     # for PimaIndiansDiabetes2 dataset
library(janitor)
library(parsnip)
library(kknn)
library(paletteer)
library(corrr)
library(scico)
library(forcats)
```

## Your Turn 1

```{r}
# Load the data
data(PimaIndiansDiabetes2)
db <- PimaIndiansDiabetes2
```

a. Tidy the data to make it ready for analysis:


```{r}

```

b. Make a correlation plot of the numerical variables in the dataset

```{r}
db %>%
  select(_____) %>%  # only numerical variables
  correlate() %>%
  stretch() %>%
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r)))) +
  scale_fill_paletteer_c("scico::roma", limits = c(-1, 1), direction = -1)

```

c. Which pair of variables in the dataset have the largest correlation?

*Answer:*


d. Using `parsnip` package perform all the steps involved in classifying whether a patient with certain glucose and insulin would have diabetes or not.


```{r}
#1 Prepare raw data
db_raw <- 

```


```{r}
# 2 Create a recipe for data pre-processing
db_recipe <- recipe(________, data = _____) %>%
  step_scale(all_predictors()) %>%
  step_center(all_predictors()) %>%
  prep()

```


```{r}
# 3 Apply the recipe to the data set
db_scaled <-  bake(______, ______)
```


```{r}
# 4 Create a model specification
knn_spec <- nearest_neighbor(mode = "classification",
                             engine = "kknn",
                             weight_func = "rectangular",
                             neighbors = 5)

```


```{r}
# 5 Fit the model on the preprocessed data
knn_fit <- knn_spec %>%
 fit( ~ ., data = )
```


```{r}
# 6 Classify
# These are standardized value!!
new_observations <- tibble(glucose = c(1, 2), insulin = c(-1, 1))
predict(, new_data = )

```

We already know the labels of some of the patients in the dataset. How well does the model predict their diabetes status? We will see more of this in the coming lectures, but for now try to compare the results for the first 10 cases in the dataset.

```{r}
some_observations <- db_scaled[1:10,1:2]
predictions <- predict(knn_fit, new_data = )
cbind(db_scaled[1:10,3], predictions)
```

What is the accuracy percentage?

*Answer:*


